### 2016-09-24 syntax.tex
moving NY comparison to its own file, and placing in an appendix

\heading{Data structures.}  We begin by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset. \jnote{I still think we should be more general, and deal
with objects other than multisets. Actually, I think we should
either specialize to sets or talk generically about data structures
for arbitrary objects; talking about multisets seems to make the
definitions more cumbersome while not adding very much in terms of
generality.}
%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$, and a collection of (multi)sets~$\calS$
over $\univ$. A \emph{data structure} (for $\calS$) is a tuple
$\setprim=(\calQ,\Rep, \Qry)$ where \jnote{I would prefer moving
$\calQ$ out of the tuple, and instead calling it a ``data structure
for $\calQ$ over $\calS$.''}:
\begin{itemize}
\item $\mathcal{Q}=\{\qry \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
\item $\Rep \colon \mathcal{S} \to \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input a (multi)set $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
    \emph{public representation data} $\pubaux \in \bits^*$ and
    \emph{private representation data} $\privaux \in \bits^*$. We write
    $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
\item $\Qry\colon \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $\pubaux,\privaux \in \bits^*$
    and a query $\qry \in \calQ$, and outputting an \emph{answer}
    $a \in \Gamma$.  We write $a \gets \Qry(\pubaux,\privaux,\qry)$
    for this execution.
\end{itemize}
\hfill\dqed
\end{definition}

@@

By setting $\Sigma=\bits^L$ for a specified $L>0$, we can capture
the so-called ``garbled Bloom filter'' due to Dong, Chen and
Wen~\cite{dong2013private}. \todo{Details have to be filled in.} This stores
xor-shares of bitstring~$x \in S$ at positions
$h_1(x),h_2(x),\ldots,h_k(x)$ in an array. Similarly, the
cuckoo-hashing construction from NY, which (loosely speaking) stores
a hash $g(x)$ at positions determined by
$h_1(x),h_2(x),\ldots,h_k(x)$, is captured when $L=|g(x)|$.
\todo{Check the correctness of this claim.}

>>>>

\heading{Data structures.}  We begin by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset. \jnote{I still think we should be more general, and deal
with objects other than multisets. Actually, I think we should
either specialize to sets or talk generically about data structures
for arbitrary objects; talking about multisets seems to make the
definitions more cumbersome while not adding very much in terms of
generality.}
%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$, and a collection of (multi)sets~$\calS$
over $\univ$. A \emph{data structure} (for $\calS$) is a tuple
$\setprim=(\calQ,\Rep, \Qry)$ where \jnote{I would prefer moving
$\calQ$ out of the tuple, and instead calling it a ``data structure
for $\calQ$ over $\calS$.''}\tsnote{But $\Qry$ really is tied to
$\calQ$, as those are the only queries upon which $\Qry$ is defined to
operate.  So, if anything, I would support removing $\calQ$ from the
high-level API, and just explaining what it is as part of the
description of $\Qry$}:
\begin{itemize}
\item $\mathcal{Q}=\{\qry \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
\item $\Rep \colon \mathcal{S} \to \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input a (multi)set $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
    \emph{public representation data} $\pubaux \in \bits^*$ and
    \emph{private representation data} $\privaux \in \bits^*$. We write
    $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
\item $\Qry\colon \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $\pubaux,\privaux \in \bits^*$
    and a query $\qry \in \calQ$, and outputting an \emph{answer}
    $a \in \Gamma$.  We write $a \gets \Qry(\pubaux,\privaux,\qry)$
    for this execution.
\end{itemize}
\hfill\dqed
\end{definition}

@@

\tsnote{needs updating, since $\Sigma$ is gone, and the range of
  $\Rep$ is just $\bits^*$ with implicit encoding of whatever is the
  ``natural'' way to think about $\pubaux$ (e.g. counters, xor-shares)}
By setting $\Sigma=\bits^L$ for a specified $L>0$, we can capture
the so-called ``garbled Bloom filter'' due to Dong, Chen and
Wen~\cite{dong2013private}. \todo{Details have to be filled in.} This stores
xor-shares of bitstring~$x \in S$ at positions
$h_1(x),h_2(x),\ldots,h_k(x)$ in an array. Similarly, the
cuckoo-hashing construction from NY, which (loosely speaking) stores
a hash $g(x)$ at positions determined by
$h_1(x),h_2(x),\ldots,h_k(x)$, is captured when $L=|g(x)|$.
\todo{Check the correctness of this claim.}
